Challenges and Recent Advances to SMT-Based Context-Bounded Model Checking for Embedded Systems

### 2016-03-19 paper.tex
fix reference
review background section

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{SMT-Based Context-Bounded Model Checking for Embedded Systems (Position Paper)}

@@

Bounded Model Checking (BMC) based on Boolean Satisfiability (SAT) was originally proposed by Biere {\it et al.} to verify hardware designs~\cite{Biere99,handbook09}. The authors were able to successfully verify digital circuits with $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by a SAT solver. BMC based on Satisfiability Modulo Theories (SMT)~\cite{BarrettSST09} was originally proposed by Armando {\it et al.}~\cite{Armando06}.

The basic idea behind BMC techniques is to check the violation of a given property at a given system's depth, {\it i.e.}, given a transition system \textit{M}, which is derived from the control-flow graph of the program; a property $\phi$ representing program correctness and/or system's behaviour; and a bound of iterations \textit{k}, which limits the loop unrolling, data structures, and context-switches in software, BMC thus unfolds the system \textit{k} times, in order to convert it into a verification condition $\psi$, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.

@@

One possible way to achieve completeness in BMC techniques is to prove that an invariant (assertion) is \textit{k}-inductive~\cite{EenS03,Sheera00}. The main challenge of such approach relies on computing and strengthening inductive invariants from the program. In particular, loop invariants computed from the program must be inductive (and not just invariant) for the corresponding VCs to be valid~\cite{Bradley07}. As a consequence, even if \textit{k}-induction procedures successfully compute such assertions, which are indeed invariant, those assertions must be inductive to prove program correctness.

There are several invariant generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also to discover the memory ``shape'' in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature even reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems using invariants generation and strengthening~\cite{Beyer15,Rocha15,Brain15}.

More specifically, in previous work, \textit{k}-induction based verification was already applied to ensure that (restricted) C programs do not contain violations related to data races~\cite{Donaldson10,Kinductor} and do respect time constraints, which were specified during the system design phase~\cite{EenS03}. Recently, Gadelha {\it et al.}, Beyer {\it et al.}, and Brain {\it et al.} presented new verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant)~\cite{Gadelha15,Beyer15}.

The \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,GrosseLD09,Sheera00}. However, there is still little evidence, in the available literature, that model checking hardware and software systems, using \textit{k}-induction (and invariants), can be efficiently exploited in embedded system verification~\cite{Rocha15,Beyer15,Brain15}. That happens due to the distinctive characteristics mentioned earlier, which influence the embedded system development and also the employed verification processes.

@@

\bibitem{xu15}
Xua X., Jiaa H., Wanga D., Yub D., Chiangc H.:
\newblock {\em Hierarchical energy management system for multi-source multi-product microgrids}
\newblock In: Renewable Energy, v. 78, pp. 621-–630, 2015.

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Challenges and Recent Advances to SMT-Based Context-Bounded Model Checking for Embedded Systems}

@@

Bounded Model Checking (BMC) based on Boolean Satisfiability (SAT) was originally proposed by Biere {\it et al.} to verify hardware designs~\cite{Biere99,handbook09}. The authors were able to successfully verify large digital circuits with approximately $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by a SAT solver. BMC based on Satisfiability Modulo Theories (SMT)~\cite{BarrettSST09} was originally proposed by Armando {\it et al.}~\cite{Armando06}.

BMC techniques aims to check the violation of a given (safety) property at a given system's depth, {\it i.e.}, given a transition system \textit{M}, which is derived from the control-flow graph of the program; a property $\phi$ that represents the program correctness and/or the system's behaviour; and a bound of iterations \textit{k}, which limits the loop unrolling, data structures, and context-switches in the program, BMC techniques thus unfold the system \textit{k} times, in order to convert it into a verification condition $\psi$, expressed in propositional logic or in a decidable-fragment of first-order logic, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.

@@

One possible way to achieve completeness in BMC techniques is to prove that an invariant (assertion) is \textit{k}-inductive~\cite{EenS03,Sheera00}. The main challenge of such approach relies on computing and strengthening inductive invariants from the program. In particular, loop invariants computed from the program must be inductive (and not just invariant) for the corresponding verification conditions to be valid~\cite{Bradley07}. As a consequence, even if \textit{k}-induction procedures successfully compute such assertions, which are indeed invariant, those must be inductive so that verifiers can automatically prove program correctness.

There are several invariant generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also to discover the memory ``shape'' in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems using invariants generation and strengthening, mostly based on interval analysis. In particular, Gadelha {\it et al.}, Beyer {\it et al.}, and Brain {\it et al.} presented new verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant)~\cite{Gadelha15,Beyer15,Brain15}.

Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10,Kinductor} considering the  Cell BE processor and (2) do respect time constraints, which are specified during the system design phase~\cite{EenS03}. The \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,GrosseLD09,Sheera00}.

However, there is still little evidence, in the available literature, that model checking hardware and software systems, using \textit{k}-induction (and invariants), can be efficiently exploited in embedded system verification. That happens due to the distinctive characteristics mentioned earlier, which influence the embedded system development and also the employed verification processes. Additionally, there is still a lack of studies for embedded software verifiers to exploit the combination of different invariant generation algorithms, including analysis to discover linear inequalities, polynomial equalities and inequalities, and facts about memory and variable aliasing~\cite{Bradley07}.

@@

\bibitem{xu15}
Xua X., Jiaa H., Wanga D., Yub D., Chiangc H.:
\newblock {\em Hierarchical energy management system for multi-source multi-product microgrids}
\newblock In: Renewable Energy, v. 78, pp. 621--630, 2015.
